Playing with PCAs

### 2024-01-11 3-reports/playing_with_pcas.Rmd
remove wte from pca. plot PCA by transect

data_combined_subset = make_data_subset(data_combined) %>% filter(!analysis %in% "LOI")
data_combined_wide_NO_DIC = make_data_wide(data_combined_subset %>% 
                                             filter(!grepl("dic", name, ignore.case = TRUE)),
                                           sample_key)
```

@@

data_combined_wide = make_data_wide(data_combined, sample_key)
data_wide_PCA = 
  data_combined_wide %>% 
  dplyr::select(-c("dic", "gwc", "percentOM")) %>% 
  rename(CEC = cec,
         NH4N = nh4n,
         NO3N = no3n,
         P = mehlichp,
         WEOC = npoc)

@@

#  ggbiplot(pca_overall$pca_int, obs.scale = 1, var.scale = 1,
#           groups = as.character(pca_overall$grp$transect), 
#           ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 0) +
#  geom_point(size=3,stroke=1, alpha = 1,
#             aes(shape = pca_overall$grp$region,
#               color = pca_overall$grp$transect))+ 
# # scale_color_manual(values = c("#16879C", "#BB281E" ))+
#  #scale_shape_manual(values = c(21, 19))+
#  #scale_shape_manual(values = c(21, 21, 19), name = "", guide = "none")+
#  # xlim(-4,20)+
#  # ylim(-8,8)+
#  labs(shape="",
#       title = "Overall PCA, both regions",
#       subtitle = "Surface horizons only")+
#  theme_kp()+
#  NULL

>>>>

data_combined_subset = make_data_subset(data_combined) # %>% filter(!analysis %in% "LOI")
data_combined_wide_NO_DIC = make_data_wide(data_combined_subset %>% 
                                             filter(!grepl("dic", name, ignore.case = TRUE)),
                                           sample_key)
```

@@

data_combined_wide = make_data_wide(data_combined_subset, sample_key)
data_wide_PCA = 
  data_combined_wide %>% 
  dplyr::select(-c("dic", "gwc", "percentOM")) %>% 
  rename(CEC = cec,
         NH4N = nh4n,
         NO3N = no3n,
         P = mehlichp,
         WEOC = npoc)

@@

  ggbiplot(pca_overall$pca_int, obs.scale = 1, var.scale = 1,
           groups = as.character(pca_overall$grp$transect), 
           ellipse = TRUE, circle = FALSE, var.axes = TRUE, alpha = 0) +
  geom_point(size=3,stroke=1, alpha = 1,
             aes(shape = pca_overall$grp$region,
               color = pca_overall$grp$transect))+ 
 # scale_color_manual(values = c("#16879C", "#BB281E" ))+
  scale_shape_manual(values = c(21, 19))+
  #scale_shape_manual(values = c(21, 21, 19), name = "", guide = "none")+
  # xlim(-4,20)+
  # ylim(-8,8)+
  labs(shape="",
       title = "Overall PCA, both regions",
       subtitle = "Surface horizons only")+
  theme_kp()+
  NULL
